### 2023-03-27 main/chapter_experiment.tex
add trigger yap paragraph

\TODO{paragraph for Table~\ref{tab:experiment_trigger_breakdown}.}

>>>>

\atlas\ implements a menu of many different triggers for specific categories of
interesting events in a representative time period.
This trigger menu includes triggers for combinations of up to three charged
leptons, one or two photons, up to six jets, up to two $b$-tagged jets, missing
transverse momentum, or hadronic states for $B$ physics.
Of these, Table~\ref{tab:experiment_trigger_breakdown} summarises the most
important trigger categories and their trigger rates under peak Run~2
operations.
In total, the peak HLT trigger rate was $1750\,\mathrm{Hz}$ for the main
physics categories, and $200\,\mathrm{Hz}$ for the $B$-physics trigger category
(which also triggers on other, non-$B$, light
states)~\cite{ATL-DAQ-PUB-2019-001}.
The $\twoljets$ search presented in this thesis uses only dilepton triggers
for electrons and muons.
As shown in Table~\ref{tab:experiment_trigger_breakdown}, these have a total
HLT trigger rate less than $105\,\mathrm{Hz}$%
\footnote{%
The listed rates overlap, so the sum of their peak rates is only an upper
bound on their union.
},
meaning that our chosen triggers cover only a few percent of \atlas's data.
